Characterizing edges in signed and vector-valued graphs

### 2017-12-21 intro/main.tex
typos

We list in \autoref{sec:outline} three concrete instantiations of this general problem that we
consider in this thesis. Our solutions to these three problems offer evidence in the defense of our
thesis statement:
\begin{quote}
\bf
There exists efficient and accurate methods to predict edge type in complex networks, relying
only on the graph topology or also on node attributes.
\end{quote}

>>>>

We list in \autoref{sec:outline} three concrete instantiations of this general problem that we
consider in this thesis. Our solutions to these three problems offer evidence in the defense of our
thesis statement:
\begin{quote}
\bf
There exist efficient and accurate methods to predict edge type in complex networks, relying
only on the graph topology or also on node attributes.
\end{quote}
